---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# D3MINFL

<!-- badges: start -->
<!-- badges: end -->

This package provides tools for performing diagnostic analysis
    on linear regression models. It includes functions to compute and plot 
    various influence measures such as Cook's Distance, DFFITS, and Hadi's 
    Influence Measure.

## Installation

You can install the development version of D3MINFL from [GitHub](https://github.com/purunnz/D3MINFL) with:

``` r
# install.packages("devtools")
devtools::install_github("purunnz/D3MINFL")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(D3MINFL)
## basic example code
```

This function calculates influence measures for a given linear model. The user can select which measure to calculate: Cook's Distance, DFFITS, or Hadi's Influence Measure.:

```{r calculate_influence_measures}
model <- lm(mpg ~ wt + hp, data = mtcars)
influence_values <- calculate_influence_measures(mtcars, model, measure = "cooks")
print(influence_values)
```

This function plots the selected influence measures for a given linear model. It combines Cook's Distance, DFFITS, and Hadi's Influence Measure in one plot.:

```{r pressure, echo = FALSE}
model <- lm(mpg ~ wt + hp, data = mtcars)
influence_values <- plot_influence_measures(mtcars, model, measure = "cooks")
plot_influence_measures(mtcars, model, measures = c("cooks", "dffits", "hadi"))
plot_influence_measures(mtcars, model, measures = "cooks")
```


